\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\usepackage{helvet}
\usepackage{url}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{fontawesome}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

%==================== Personal Info ====================%

\name{Hiruni Sandamini} % <-- Replace with your full name
\address{\faPhone\ +94 71 796 6068 \quad \faEnvelope\ herathliyanagehs@gmail.com \quad \faGlobe\ \href{https://hsandamini.github.io/MyPortfolio/}{Portfolio}}
\address{\faMapMarker\ Ja-Ela, Sri Lanka} % <-- Replace with your location

\begin{document}

%==================== Education ====================%

\begin{rSection}{Education}

{\bf University of Sri Jayewardenepura} \hfill {\em May 2023 - Present} 
\\ B.Sc. (Honours) in Statistics \textbf{(Reading)} \hfill { CGPA: 3.36/4.00}
\\ Department of Statistics \\

\end{rSection}

%==================== Skills ====================%
\begin{rSection}{Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming & R, Python, SQL \\
R Packages & tidyverse, readr, caret, shiny, forecast \\
Software \& Tools & Minitab, EViews, Microsoft Office, \LaTeX \\
Data Visualization Tools & R (ggplot2, plotly, flexdashboard)\\
Statistics Coursework & Probability and Distribution Theory I \& II, Data Analysis I \& II, \\
& Statistical Communication, Sampling Techniques, Design and Analysis of \\
& Experiments, Time Series Analysis, Multivariate Statistical Methods, \\
& Discrete \& Categorical Data Analysis, Advanced Design of Experiments, \\
& Advanced Distribution Theory, Essential Skills in Statistics, \\
& Statistical Quality Assurance, Medical Statistics, Introduction to \\
& Actuarial Statistics, Stochastic Processes, Generalized Linear and \\
& Non-Linear Models, Spatial Data Analysis \\
Mathematics Coursework & Differential Equations, Complex Numbers and Vectors, Linear Algebra \\
& I \& II, Calculus, Vector Calculus, Numerical Methods \\
Economics Coursework & Principles of Microeconomics, Principles of Macroeconomics, \\
& Environmental Economics, Intermediate Microeconomics, Intermediate \\
& Macroeconomics \\
\end{tabular}
\end{rSection}

%==================== Work Experience ====================%

\begin{rSection}{Work Experience}
\begin{rSubsection}{Transfer Operations \& Booking Coordinator}{December 2022 - April 2023}{T2 Transfer, Paris, France (Remote)}{}
\item Managed airport transfer bookings, confirmed reservations via email, and maintained daily schedules. Monitored flight updates and communicated changes to ensure smooth coordination between customers, drivers, and the operations team.
\end{rSubsection}
\end{rSection}

%==================== Projects ====================%

\begin{rSection}{Projects}

\begin{rSubsection}{New Zealand Health \& Demographics Dashboard}{March 2026}{}{}
\item Developed an interactive dashboard using R Shiny to analyze health, epidemiology, and demographic trends in New Zealand.
\item Visualized population trends, fertility rates, mortality rates, age distribution, and key health indicators. \href{https://hiruniherath.shinyapps.io/Rshiny_app_NewZealand_health_dashboard/}{View Dashboard}
\end{rSubsection}

\begin{rSubsection}{QA \& Performance Dashboard}{January 2026 }{}{}
\item Built an interactive dashboard using R Shiny to monitor QA metrics and process performance.
\item Implemented \={X} and R control charts to assess process stability and variation.
\item Enabled data upload and exportable visual reports.
\href{https://hiruniherath.shinyapps.io/Downloads/}{View Dashboard}
\end{rSubsection}

\begin{rSubsection}{
Analysis of Factors Impacting Export Performance in Sri Lanka\\
{\small\textit{Unpublished Group Research Project}}
}{October 2025}{}{}
\item Analyzed monthly data (2007–2024) to identify key drivers of export performance in Sri Lanka.
\item Applied multiple linear regression to evaluate the impact of imports, exchange rate, and crude oil prices on export growth.
\href{https://drive.google.com/file/d/1z7Mu97fLYHxbJ5bMiPOJsT1EK2aqRTsy/view}{View Research Report}
\end{rSubsection}

\begin{rSubsection}{Mini Project: Applications of Bivariate Distribution \& Order Statistics}{}{}{}
\item Conducted a literature-based study on bivariate distributions and order statistics using published journal articles.
\item Reviewed applications in rainfall–temperature modeling and extreme value analysis (GEV).
\item Proposed a novel conceptual application of order statistics to optimize grocery shopping efficiency.
\href{https://drive.google.com/file/d/1ztKpnNdySo7BiQfbNkcDytvZhxpFplL6/view}{View Report}
\end{rSubsection}

\end{rSection}

%==================== Certificates ==============%

\begin{rSection}{Certificates}

\begin{rSubsection}{Certificate of Completion – C Programming for Beginners}{June 2023}{}{}
\item Completed C Programming for Beginners course at Great Learning Academy.
\href{https://drive.google.com/file/d/17yBkDsDMljyqSySPbw4xm5KKSup34ilK/view}{View Certificate}
\end{rSubsection}

\begin{rSubsection}{Certificate in English – Intermediate Level}{July 2022}{}{}
\item Completed Intermediate Level English course at BCI Campus, Negombo.
\href{https://drive.google.com/file/d/1i6qYmFqPSjXAUdLu2JxqDj3YJeBDll6S/view}{View Certificate}
\end{rSubsection}

\end{rSection}

%==================== Awards ====================%

\begin{rSection}{Achievements} 

\begin{rSubsection}{Champion – Inter-Unit Carol Competition (Team Event)}{2023}{}{}
\item Vox Nathalista Carol Service \& Competition, SLUCSM,  Colombo Region.
\href{https://drive.google.com/file/d/1TiQX5Kn3mH6cxvPmqFG7c-65bgySLIHT/view}{View Certificate}
\end{rSubsection}

\end{rSection}


%==================== Referees ====================%

\begin{rSection}{Referees} 
\begin{multicols}{2}
\noindent
\textbf{Dr. Manjula Perera} \\
\textit{Lecturer, Department of Statistics} \\
University of Sri Jayewardenepura \\
Sri Lanka \\
+94 77 636 7955 \\
\texttt{manjula@sjp.ac.lk}

\columnbreak

\noindent
\textbf{Dr. Chathuri Jayasinghe} \\
\textit{Senior Lecturer, Department of Statistics} \\
University of Sri Jayewardenepura \\
Sri Lanka \\
+94 77 699 1982 \\
\texttt{chathuri@sjp.ac.lk}
\end{multicols}

\end{rSection}

\end{document}
